Short-term neuronal and synaptic plasticity act in synergy for deviance detection in spiking networks

### 2023-02-06 paper-1/manuscript.tex
editing

Here, we investigate how neuronal threshold adaptation can lead to deviance detection. Specifically, we use a spatially constrained, randomly connected network of point neurons with spike-triggered threshold adaptation, and show that deviance detection emerges from this mechanism alone, requiring neither synaptic plasticity nor a tightly defined network structure. Furthermore, we model the conjunction of both neuronal and synaptic short-term plasticity, and study how these mechanisms interact within the network as it processes regular and irregular stimulus sequences.

>>>>

Here, we investigate how neuronal threshold adaptation can lead to deviance detection. Specifically, we use a spatially constrained, randomly connected network of point neurons with spike-triggered threshold adaptation and show that deviance detection emerges from this mechanism alone, requiring neither synaptic plasticity nor a tightly defined network structure. Furthermore, we model the conjunction of both neuronal and synaptic short-term plasticity, and study how these mechanisms interact within the network as it processes regular and irregular stimulus sequences.
